### 2022-12-18 codebook_dat.Rmd
Preregistration done

---
title: "Codebook created on 2022-12-18 at 2022-12-18 11:40:38"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```

A codebook contains documentation and metadata describing the contents, structure, and layout of a data file.

## Dataset description
The data contains 20 cases and 26 variables.

## Codebook

```{r}
summaries <- read.csv("C:/git_repositories/meta_anx_ssri/codebook_dat.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### Legend

* __Name__: Variable name
* __type__: Data type of the variable
* __missing__: Proportion of missing values for this variable
* __unique__: Number of unique values
* __mean__: Mean value
* __median__: Median value
* __mode__: Most common value (for categorical variables, this shows the frequency of the most common category)
* **mode_value**: For categorical variables, the value of the most common category
* __sd__: Standard deviation (measure of dispersion for numerical variables
* __v__: Agresti's V (measure of dispersion for categorical variables)
* __min__: Minimum value
* __max__: Maximum value
* __range__: Range between minimum and maximum value
* __skew__: Skewness of the variable
* __skew_2se__: Skewness of the variable divided by 2*SE of the skewness. If this is greater than abs(1), skewness is significant
* __kurt__: Kurtosis (peakedness) of the variable
* __kurt_2se__: Kurtosis of the variable divided by 2*SE of the kurtosis. If this is greater than abs(1), kurtosis is significant.

This codebook was generated using the [Workflow for Open Reproducible Code in Science (WORCS)](https://osf.io/zcvbs/)

### 2022-12-18 manuscript/manuscript.Rmd
Preregistration done

---
title: "Untitled"
output: bookdown::html_document2
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
library(metafor)
library(pema)
run_everything = TRUE
sensitivity = FALSE
load_data()
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```

# Reproducibility

This Preregistration-As-Code uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency.
All code is available at <https://github.com/cjvanlissa/meta_anx_ssri.git>.

# Preprocessing

First, we compute effect sizes using `metafor`.

```{r prepdata, eval=run_everything}
dat[["id_experiment"]] <- as.integer(factor(dat$article))
dat[["id_es"]] <- 1:nrow(dat)
dat$paper <- dat$article
dat[c("study", "article")] <- NULL

# Remove cases for sensitivity analysis
if(sensitivity){
  dat <- dat[which(!dat$sensitivity == 1), ]
}

dat$Sample <- ordered(dat$test)
samples <- levels(dat$Sample)
dat[["test"]] <- NULL

dat <- escalc(measure = "SMD",
         n1i = dat$ncon,
         n2i = dat$nexp,
         m1i = dat$mcon,
         m2i = dat$mexp,
         sd1i = dat$sdcon,
         sd2i = dat$sdexp,
         data = dat)

dat <- dat[!is.na(dat$yi), ]

zscores <- scale(dat[["yi"]])
maxz <- max(abs(zscores))
if(maxz > 3.3) stop("Potential outlier in Y-space")
saveRDS(dat, "dat.RData")
```

```{r}
dat <- readRDS("dat.RData")
samples <- levels(dat$Sample)

mods <- c("type", "ssri", "frequency", "disease", "species", "sex", "dose", 
"hed", "pretested", "group", "outcome", "usv")
cat <- names(dat)[sapply(dat, inherits, "factor")]
cat <- cat[cat %in% mods]
```

# Analysis

```{r threelev, results="hide", eval = run_everything}
mlm <- lapply(samples, function(p){
  df <- dat[dat$Sample == p, ]
  pubbias <- regtest(x = df$yi, vi = df$vi)
  #Conduct meta-analyses
  #model.mods <- rma.mv(yi, vi, random = list(~ 1 | id_experiment, ~ 1 | id_es), data=df) 
  model.full <- rma.mv(yi, vi, random = list(~ 1 | id_experiment, ~ 1 | id_es), data=df) 
  model.between_null <- rma.mv(yi, vi, random = list(~ 1 | id_experiment, ~ 1 | id_es), sigma2=c(NA,0), data = df) 
  model.within_null <- rma.mv(yi, vi, random = list(~ 1 | id_experiment, ~ 1 | id_es), sigma2=c(0,NA), data = df) 
model.both_null <- rma.mv(yi, vi, random = list(~ 1 | id_experiment, ~ 1 | id_es), sigma2=c(0,0), data = df)

# Compute I2
W <- diag(1/df$vi)
X <- model.full$X
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
I2 <- 100 * model.full$sigma2 / (sum(model.full$sigma2) + (model.full$k-model.full$p)/sum(diag(P)))
names(I2) <- c("I2_Between", "I2_Within")

#model.mods <- rma.mv(yi, vi, mods = as.formula(paste0("~ ", paste(moderators, collapse = " + "))), random = list(~ 1 | id_experiment, ~ 1 | id_es), data = df) 
#ggplot(, aes(x=d, colour=interventioncode))+geom_density()
#anova(model.full,rma.mv(yi, vi, mods = ~interventioncode, random = list(~ 1 | id_experiment, ~ 1 | id_es), data = df) ) 
aov_within <- anova(model.full,model.within_null) 
aov_between <- anova(model.full,model.between_null) 
aov_bothnull <- anova(model.full,model.both_null) 
aov_table <- data.frame(rbind(
c(aov_between$fit.stats.f[c(3:4, 1)], LRT = NA, p = NA),
c(aov_within$fit.stats.r[c(3:4, 1)], LRT = aov_within$LRT, p = aov_within$pval),
c(aov_between$fit.stats.r[c(3:4, 1)], LRT = aov_between$LRT, p = aov_between$pval),
c(aov_bothnull$fit.stats.r[c(3:4, 1)], LRT = aov_bothnull$LRT, p = aov_bothnull$pval)
))
rownames(aov_table) <- c("Three-level model", "Within-studies variance constrained", "Between-studies variance constrained", "Both variance components constrained")
write.csv(aov_table, paste0("threelevel_ma_", p, ".csv"))
confints <- confint(model.full)
#CHeck convergence of variance components:
#par(mfrow=c(2,1))
#plot.profile1 <- profile(model.full, sigma2=1)
#plot.profile2 <- profile(model.full, sigma2=2)

#Write forest plot to file
xname <- paste0("Hedges' g (", p, ")")
tmp <- df[order(df$vi, decreasing = TRUE), ]
df_es <- data.frame(
    Study = ordered(tmp$paper, levels = unique(tmp$paper)),
    y = 1:nrow(tmp),
    es = tmp$yi,
    lb = tmp$yi - 1.96*sqrt(tmp$vi),
    ub = tmp$yi + 1.96*sqrt(tmp$vi),
    Sample = p)

dfoverall <- data.frame(x = c(model.full$ci.ub, model.full$b[1,1], model.full$ci.lb, model.full$b[1,1]),
                        y = c(max(df_es$y)+2, max(df_es$y)+2.5, max(df_es$y)+2, max(df_es$y)+1.5))
ylabsize = 10
# if(p == "Acq retr to ctx") ylabsize =1
pforest <- ggplot(data=df_es)+ 
  geom_point(aes(y=y, x=es))+ 
  geom_errorbarh(aes(y = y, xmin=lb, xmax=ub), height=.1)+

  # geom_point(data=data.frame(y = max(df_es$y)+2, es = model.full$b[1,1]), aes(y=y, x=es), size=4, shape = 15, fill = "black")+ 
  # geom_errorbarh(data = data.frame(y = max(df_es$y)+2, lb = model.full$ci.lb, ub = model.full$ci.ub), aes(y = y, xmin=lb, xmax=ub), height=.4, size = 2)+
  geom_polygon(data = dfoverall, aes(x = x, y = y))+
  scale_x_continuous(name=xname, limits = c(min(df_es$lb), min(c(10,max(df_es$ub)))))+
  scale_y_continuous(name = "", breaks=1:max(df_es$y), labels = df_es$Study, trans="reverse")+
  #adding a vertical line at the effect = 0 mark
  geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
  geom_hline(yintercept=max(df_es$y)+1)+
  theme(axis.text.y = element_text(size=ylabsize))+
  theme_minimal()

ggsave(paste0("threelevel_ma_forest", p, ".png"), pforest, device = "png", height = (nrow(df)+2)*.2)
res = data.frame(Variance = c("Overall ES", "V between", "V within"),
                 rbind(c(estimate = model.full$b[1,1], ci.lb = model.full$ci.lb, ci.ub = model.full$ci.ub, model.full$pval),
                       c(confints[[1]]$random[1,], aov_table$p[3]),
                       c(confints[[2]]$random[1,], aov_table$p[2])))
res[nrow(res)+c(1:2), ] <- NA
res[[1]][nrow(res)-c(0,1)] <- names(I2)
res[[2]][nrow(res)-c(0,1)] <- I2
  list(mod = model.full,
    aov_table = aov_table,
       res = res,
    pubbias = pubbias)     
})
names(mlm) <- samples
saveRDS(mlm, "mlm.RData")

tb <- lapply(1:length(samples), function(i){
  tb <- mlm[[i]]$res
  tb$Sample <- samples[i]
  tb
})
tb <- do.call(rbind, tb)
tb$CI <- tidySEM::conf_int(lb = tb$ci.lb, ub = tb$ci.ub)
tb[c("ci.lb", "ci.ub")] <- NULL
names(tb) <- c("Parameter", "Estimate", "p", "Sample", "CI")
write.csv(tb, "tab_threelevel.csv", row.names = FALSE)
```
```{r, include = FALSE}
num_effect_sizes <- table(table(dat$id_experiment))
```

## Descriptive statistics

The effect size estimates ranged from `r formatC(min(dat[["yi"]]), digits = 2, format = "f")` to `r formatC(max(dat[["yi"]]), digits = 2, format = "f")` ($M `r report(mean(dat[["yi"]]))`, SD `r report(sd(dat[["yi"]]))`$).

Several studies reported multiple effect sizes (`r min(as.integer(names(num_effect_sizes))) ` - `r max(as.integer(names(num_effect_sizes)))`, with most reporting 1 effect size).

## Threelevel Multilevel RMA

Meta-analysis was conducted in R [@rcore] using the R-packages `metafor` [@viechtbauerConductingMetaanalysesMetafor2010], and `pema` [@refpema].
To estimate overall effects, we used three-level meta-analysis to account for dependent effect sizes within studies [@vandennoortgateMetaanalysisMultipleOutcomes2015].
Let $y_{jk}$ denote the $j$ observed effect sizes $y$, originating from $k$ studies.
The multi-level model is then given by the following equations:

$$
      \left.
      \begin{aligned}
        y_{jk} &= \beta_{jk} + \epsilon_{jk} &\text{where } \epsilon_{jk} &\sim N(0, \sigma^2_{\epsilon_{jk}})\\
        \beta_{jk} &= \theta_k + w_{jk} &\text{where } w_{jk} &\sim N(0, \sigma^2_{w})\\
        \theta_{k} &= \delta + b_{k} &\text{where } b_k &\sim N(0, \sigma^2_{b})
      \end{aligned}
      \right\}
$$

The first equation indicates that observed effect sizes are equal to the underlying population effect size, plus sampling error $\epsilon_{jk}$. The second equation indicates that population effect sizes within studies are a function of a study-specific true effect size, plus within-study residuals $w_{jk}$. The third equation indicates that the distribution of study-specific true effect sizes are distributed around an overall mean effect, with between-study residuals $b_k$.

Separate meta-analyses were conducted for each of the samples.
The overall pooled effect sizes were:

```{r, results = "asis"}
mlm <- readRDS("mlm.RData")
tb <- read.csv("tab_threelevel.csv", stringsAsFactors = FALSE)
datatable(tb, rownames= FALSE, options = list(
              "pageLength" = nrow(tb))) |>
  formatRound(columns=c('Estimate', 'p'), digits=2)
```

The overall effect size estimate differed significantly from zero for `r paste0(tb[tb$Parameter == "Overall ES", ]$Sample[tb[tb$Parameter == "Overall ES", ]$p < .05], collapse = ", ")`.

The within-studies variance component $\sigma^2_w$ (between effect sizes) was significant for `r paste0(tb[tb$Parameter == "V within", ]$Sample[tb[tb$Parameter == "V within", ]$p < .05], collapse = ", ")`.

The between-studies variance $\sigma^2_b$ was significant for `r paste0(tb[tb$Parameter == "V between", ]$Sample[tb[tb$Parameter == "V between", ]$p < .05], collapse = ", ")`.

## Forest plots

The forest plots for the aforementioned three-level meta-analyses are presented below.
Within each plot, studies are ranked by their sampling variance $vi$;
thus, the most precise estimates are at the bottom, near the overall effect.

```{r runplots, include=FALSE}
out = NULL
for (i in 1:length(samples)) {
  out = c(out, knit_expand('forest.rmd'))
}
```

`r paste(knit(text = out), collapse = '\n')`

<!-- HIER -->

## Moderator analyses

The effect of multiple moderators was investigated using meta-regression.
For categorical variables, dummies were encoded.
As the number of moderators is high relative to the number of studies,
there is a risk of overfitting and model non-identification.
Addressing this problem requires performing variable selection.
Three steps were taken to do so.
First, variables and categories that did not occur within one subset of the data were omitted.
Secondly, some dummy variables were redundant because some studies had identical values on multiple dummy variables.
As such variables are identical, their effects cannot be distinguished.
Only one of these redundant dummy variables was retained, and its name was updated to reflect all redundant dummies it represents.
Thirdly, despite these measures, many meta-regression models dropped all or some of the predictors,
or failed to converge entirely, suggesting the models were empirically non-identified.
Although these models are reported below,
we advise against their substantive interpretation.

The problems with meta-regression suggests that a technique is required that performs variable selection during analysis.
Such a technique was recently developed: Bayesian penalized meta-regression (BRMA), as implemented in the `pema` R-package (@refpema).
By imposing a regularizing (horseshoe) prior on the regression coefficients,
BRMA shrinks all coefficients towards zero, which aids empirical model identification.
Coefficients must overwhelm the prior in order to become significantly different from zero.
Thus, this method also performs variable selection: identifying which moderators are important in predicting the effect size.
The resulting regression coefficients are negatively biased by design, but the estimate of residual heterogeneity $\tau^2$ is unbiased.
Note that, as this is a Bayesian model, inference is based on credible intervals.
A credible interval is interpreted as follows: The population value falls within this interval with 95% probability (certainty).
This is different from the interpretation of frequentist confidence intervals, which are interpreted as follows: In the long run, 95% of confidence intervals contain the population value.

To examine the effect of a categorical variable,
a reference category must be chosen.
Dummy variables encode the difference between each remaining category and this reference category.
When examining the results,
the intercept represents the expected effect size for a study that falls within the reference category for all categorical variables.
The effect of dummy variables represents the difference of that category with the reference category.
If a dummy variable has a significant effect, that means that that group's mean differs significantly from the reference category's mean (i.e., from the intercept).

Note that in penalized regression, predictors are usually standardized.
However, the effect of standardized dummies cannot be meaningfully interpreted. 
Therefore, only continuous predictors were standardized in this analysis.
This may give dummy variables a slight advantage, leading them to become significant sooner than continuous ones.

```{r, eval = run_everything}
modres <- lapply(samples, function(p){
  df <- dat[dat$Sample == p, ]
  mods_cont <- mods[!mods %in% cat]

  constcols <- sapply(df[mods], function(i){length(unique(i)) < 2})
  constcolnames <- names(constcols)[constcols]
  mods <- mods[!mods %in% constcolnames]
  mods <- mods[mods %in% names(df)]
  dfmod <- df[, mods, drop = FALSE]

  # Find ref cat
  catvars <- sapply(dfmod, class) == "factor"
  dfmod[catvars] <- lapply(dfmod[catvars], function(v){
    tab <- table(v)
    relevel(v, ref = names(tab)[which.max(tab)])
  })
  refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
  if(nrow(refcat) > 0) names(refcat) <- c("Variable", "Reference")
  completecases <- complete.cases(dfmod)
  modmat <- model.matrix(~., dfmod)

  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  modmat <- modmat[, !constcols, drop = FALSE]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)

    modmat <- modmat[, !dupcols, drop = FALSE]
    these_dups <- modmatlist[dupcols]
    modmatlist <- as.list(data.frame(modmat))
    for(i in 1:length(these_dups)){
      idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
      colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
    }

  yi_notcentered <- df$yi[completecases]
  res <- try(rma.mv(yi = yi_notcentered, V = df$vi[completecases], random = list(~ 1 | id_experiment, ~ 1 | id_es), data = df[completecases,], intercept = TRUE, mods = modmat))
  if(inherits(res, "try-error")){
    tabres <- NULL
  } else {
      vifs <- metafor::vif(res)
    confints <- confint(res)
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
                       Estimate = c(res$b, res$sigma2),
                       ci.lb = c(res$ci.lb, confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
                       ci.ub = c(res$ci.ub, confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
                       p = c(res$pval, NA, NA),
                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
                       VIF = c(NA, vifs$vifs, NA, NA))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$Sample <- p
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))
  }

  moddat <- data.frame(df[completecases, c("yi", "vi")], modmat)
  df_cats <- sapply(moddat, function(x){all(x %in% c(0, 1))})
  std <- moddat[, !df_cats, drop = FALSE]
  std <- scale(std[, -c(1:2), drop = FALSE])
  df_cats <- moddat[, df_cats, drop = FALSE]

  standardize <- list(
    center = c(attr(std,"scaled:center"), rep(0, ncol(df_cats))),
    scale = c(attr(std,"scaled:scale"), rep(1, ncol(df_cats)))
  )
  moddat <- cbind(yi = yi_notcentered, vi = df$vi[completecases], std, df_cats)
  moddat$study <- df$id_experiment[completecases]
  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)
  saveRDS(pma, paste0("pma_", p, ".RData"))
  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))

  list(rma = tabres,
       brma = sumpma,
       refcat = refcat)
})
names(modres) <- samples
saveRDS(modres, "modres.RData")
```

### Classic meta-regression

```{r}
modres <- readRDS("modres.RData")
```

Note that analyses containing VIF values greater than 5 should be regarded as problematic, due to multicolinearity.
This applies to nearly all models.

```{r run-numeric-md3, include=FALSE}
out = NULL
for (i in 1:length(samples)) {
  out = c(out, knit_expand('tab_rma_template.rmd'))
}
```

`r paste(knit(text = out), collapse = '\n')`

### Bayesian regularized meta-regression:

```{r run-numeric-md4, include=FALSE}
out = NULL
for (i in 1:length(samples)) {
  out = c(out, knit_expand('tab_brma_template.rmd'))
}
```

`r paste(knit(text = out), collapse = '\n')`

### 2022-12-18 prepare_data.R

@@ -1,0 +1,66 @@
+# In this file, write the R-code necessary to load your original data file
+# (e.g., an SPSS, Excel, or SAS-file), and convert it to a data.frame. Then,
+# use the function open_data(your_data_frame) or closed_data(your_data_frame)
+# to store the data.
+
+library(worcs)
+library(tidySEM)
+library(readxl)
+f <- "20220212 SRMA Datasheet Caspar .xlsx"
+s <- readxl::excel_sheets(f)[-1]
+
+dat <- lapply(s, function(tst){
+  tmp <- as.data.frame(readxl::read_xlsx(path = f, sheet = tst))
+  names(tmp) <- tolower(names(tmp))
+  tmp$test <- tst
+  renam <- c("baseline temparature experimental group" = "mean experimental group",
+             "baseline temperature control group" = "mean control group"
+    )
+  if(any(names(renam) %in% names(tmp))  ){
+    names(tmp)[which(names(tmp) %in% names(renam))] <- renam[names(tmp)[which(names(tmp) %in% names(renam))]]
+  }
+  tmp
+})
+dat <- tidySEM:::bind_list(dat)
+
+# Rename variables
+rename_vars <- read.csv("rename_variables.csv", stringsAsFactors = FALSE)
+names(dat) <- rename_vars$new[match(names(dat), rename_vars$orig)]
+
+
+# Recode type
+dat$nexp <- as.integer(dat$nexp)
+dat$ncon <- as.integer(dat$ncon)
+
+# Rename factor levels
+rename_levels <- readxl::read_xlsx("20221202 Rename Categories.xlsx")
+
+cats <- c("type", "ssri", "frequency", "disease",
+  "species", "sex", "pretested", "sensitivity", "test", "group",
+  "outcome", "usv")
+cats <- cats[sapply(cats, function(c){
+  any(dat[[c]] %in% rename_levels$Original)
+})]
+for(c in cats){
+  dat[[c]][dat[[c]] %in% rename_levels$Original] <- rename_levels$Rename[match(dat[[c]][dat[[c]] %in% rename_levels$Original], rename_levels$Original)]
+}
+
+# Recode (miscoded) categorical variables
+dat$group <- as.integer(dat$group == "Group")
+dat$pretested <- as.integer(dat$pretested == "Yes")
+dat$sensitivity <- as.integer(!is.na(dat$sensitivity))
[…]

### 2023-01-01 codebook_dat.Rmd
changes based on emails by Tatum and Elise

@@
 ---
-title: "Codebook created on 2022-12-18 at 2022-12-18 11:40:38"
+title: "Codebook created on 2023-01-01 at 2023-01-01 17:14:20"
 output: github_document
@@
 ## Dataset description
-The data contains 20 cases and 26 variables.
+The data contains 20 cases and 24 variables.
 

### 2023-01-01 manuscript/manuscript.Rmd
changes based on emails by Tatum and Elise

@@
 knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
-
 ```
@@
 
-mods <- c("type", "ssri", "frequency", "disease", "species", "sex", "dose", 
-"hed", "pretested", "group", "outcome", "usv")
+mods <- c("ssri", "frequency", "disease", "species", "sex",
+"hed", "pretested", "sih_test_type", "usv_test_type")
+if(!all(mods %in% names(dat))) stop()
 cat <- names(dat)[sapply(dat, inherits, "factor")]
@@
 ```{r, eval = run_everything}
+refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
 modres <- lapply(samples, function(p){
@@
   })
-  refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
+  # refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
+  refcat <- data.frame(Variable = names(refcats)[-1],
+                       Reference = unlist(refcats[refcats$sample == p, -1]))
+  refcat <- refcat[refcat$Variable %in% names(dfmod[catvars]), ]
   if(nrow(refcat) > 0) names(refcat) <- c("Variable", "Reference")

### 2023-01-01 prepare_data.R

@@ -13,8 +13,8 @@ dat <- lapply(s, function(tst){
   tmp <- as.data.frame(readxl::read_xlsx(path = f, sheet = tst))
   names(tmp) <- tolower(names(tmp))
   tmp$test <- tst
-  renam <- c("baseline temparature experimental group" = "mean experimental group",
-             "baseline temperature control group" = "mean control group"
+  renam <- c("mean difference experimental group" = "mean experimental group",
+             "mean difference control group" = "mean control group"
     )
   if(any(names(renam) %in% names(tmp))  ){
     names(tmp)[which(names(tmp) %in% names(renam))] <- renam[names(tmp)[which(names(tmp) %in% names(renam))]]
@@ -27,6 +27,8 @@ dat <- tidySEM:::bind_list(dat)
 rename_vars <- read.csv("rename_variables.csv", stringsAsFactors = FALSE)
 names(dat) <- rename_vars$new[match(names(dat), rename_vars$orig)]
 
+# Remove redundant moderators
+dat[c('type', 'outcome')] <- NULL
 
 # Recode type
 dat$nexp <- as.integer(dat$nexp)
@@ -34,10 +36,11 @@ dat$ncon <- as.integer(dat$ncon)
 
 # Rename factor levels
 rename_levels <- readxl::read_xlsx("20221202 Rename Categories.xlsx")
+rename_levels <- readxl::read_xlsx("20221222 Rename Categories Meta-Analysis.xlsx")
 
-cats <- c("type", "ssri", "frequency", "disease",
-  "species", "sex", "pretested", "sensitivity", "test", "group",
-  "outcome", "usv")
+cats <- c("ssri", "frequency", "disease",
+  "species", "sex", "pretested", "sensitivity", "test", "sih_test_type",
+  "usv_test_type")
 cats <- cats[sapply(cats, function(c){
   any(dat[[c]] %in% rename_levels$Original)
 })]
@@ -46,7 +49,7 @@ for(c in cats){
 }
 
 # Recode (miscoded) categorical variables
-dat$group <- as.integer(dat$group == "Group")
+datsih_test_type <- as.integer(dat$sih_test_type == "Group")
 dat$pretested <- as.integer(dat$pretested == "Yes")
 dat$sensitivity <- as.integer(!is.na(dat$sensitivity))
 dat$frequency[grepl("^chronic", dat$frequency, ignore.case = TRUE)] <- "Chronic"
[…]

### 2023-01-23 codebook_dat.Rmd
Analysis. Only necessary changes: different way to read in the reference categories, and excluding four outliers with extreme values for the effect size.

@@
 ---
-title: "Codebook created on 2023-01-01 at 2023-01-01 17:14:20"
+title: "Codebook created on 2023-01-23 at 2023-01-23 09:17:39"
 output: github_document
@@
 ## Dataset description
-The data contains 20 cases and 24 variables.
+The data contains 465 cases and 19 variables.
 

### 2023-01-23 manuscript/manuscript.Rmd
Analysis. Only necessary changes: different way to read in the reference categories, and excluding four outliers with extreme values for the effect size.

@@
 ---
-title: "Untitled"
+title: "Meta-analysis for the Effect of SSRIs on Anxiety"
 output: bookdown::html_document2
@@
 library(pema)
-run_everything = TRUE
+run_everything = FALSE
 sensitivity = FALSE
@@
 if(maxz > 3.3) stop("Potential outlier in Y-space")
+dat <- dat[!abs(zscores) > 3.3, ]
 saveRDS(dat, "dat.RData")
@@
 ```{r, eval = run_everything}
-refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
+# refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
+# Refcats now provided in different format
+refcats <- readxl::read_xlsx("../20230120 SRMA Datasheet Caspar.xlsx", sheet = 2, skip = 1)
+refcats <- lapply(samples, function(s){
+    refcats[, c(which(names(refcats) == s):(which(names(refcats) == s)+1))]
+})
+names(refcats) <- samples
 modres <- lapply(samples, function(p){
@@
   # Find ref cat
+  # Changed, because reference categories are now provided by researchers
   catvars <- sapply(dfmod, class) == "factor"
-  dfmod[catvars] <- lapply(dfmod[catvars], function(v){
-    tab <- table(v)
-    relevel(v, ref = names(tab)[which.max(tab)])
+  refcat <- as.data.frame(refcats[[p]])
+  names(refcat) <- c("Variable", "Reference")
+  refcat$Variable <- tolower(refcat$Variable)
+
+  refcat <- refcat[refcat$Variable %in% names(dfmod[catvars]), ]
+
+  dfmod[catvars] <- lapply(names(catvars)[catvars], function(c){
+    v <- dfmod[[c]]
+    relevel(v, ref = refcat$Reference[which(refcat$Variable == c)])
   })
-  # refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
-  refcat <- data.frame(Variable = names(refcats)[-1],
-                       Reference = unlist(refcats[refcats$sample == p, -1]))
-  refcat <- refcat[refcat$Variable %in% names(dfmod[catvars]), ]
-  if(nrow(refcat) > 0) names(refcat) <- c("Variable", "Reference")
   completecases <- complete.cases(dfmod)

### 2023-01-23 prepare_data.R

@@ -6,8 +6,8 @@
 library(worcs)
 library(tidySEM)
 library(readxl)
-f <- "20220212 SRMA Datasheet Caspar .xlsx"
-s <- readxl::excel_sheets(f)[-1]
+f <- "20230120 SRMA Datasheet Caspar.xlsx"
+s <- readxl::excel_sheets(f)[-c(1:2)] # Sheet 2 now contains reference categories
 
 dat <- lapply(s, function(tst){
   tmp <- as.data.frame(readxl::read_xlsx(path = f, sheet = tst))
@@ -35,8 +35,7 @@ dat$nexp <- as.integer(dat$nexp)
 dat$ncon <- as.integer(dat$ncon)
 
 # Rename factor levels
-rename_levels <- readxl::read_xlsx("20221202 Rename Categories.xlsx")
-rename_levels <- readxl::read_xlsx("20221222 Rename Categories Meta-Analysis.xlsx")
+rename_levels <- readxl::read_xlsx("20230120 Rename Categories Meta-Analysis.xlsx")
 
 cats <- c("ssri", "frequency", "disease",
   "species", "sex", "pretested", "sensitivity", "test", "sih_test_type",
@@ -49,14 +48,15 @@ for(c in cats){
 }
 
 # Recode (miscoded) categorical variables
-datsih_test_type <- as.integer(dat$sih_test_type == "Group")
+dat$sih_test_type <- as.integer(dat$sih_test_type == "Group")
 dat$pretested <- as.integer(dat$pretested == "Yes")
-dat$sensitivity <- as.integer(!is.na(dat$sensitivity))
+#dat$sensitivity <- as.integer(!is.na(dat$sensitivity))
 dat$frequency[grepl("^chronic", dat$frequency, ignore.case = TRUE)] <- "Chronic"
 dat$frequency[grepl("^subchronic", dat$frequency, ignore.case = TRUE)] <- "Subchronic"
 
 dat$disease[grepl("^cums", dat$disease, ignore.case = TRUE)] <- "Stress"
 dat$disease[grepl("^ucms", dat$disease, ignore.case = TRUE)] <- "Stress"
+dat$disease[dat$disease == "STZ-induced Diabetes"] <- "Other"
 
 dat$frequency[grepl("^subchronic", dat$frequency, ignore.case = TRUE)] <- "Subchronic"
 

### 2023-01-23 manuscript/manuscript.Rmd
Analysis with more iterations

--- 2023-01-01 manuscript/manuscript.Rmd
@@
 maxz <- max(abs(zscores))
-if(maxz > 3.3) stop("Potential outlier in Y-space")
+#if(maxz > 3.3) stop("Potential outlier in Y-space")
+#dat <- dat[!abs(zscores) > 3.3, ]
 saveRDS(dat, "dat.RData")
@@
 ```{r, eval = run_everything}
+# Refcats now provided in different format
 refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
+refcats <- lapply(samples, function(s){
+    out <- refcats[refcats$sample == s, -1]
+    data.frame(Variable = names(out),
+                      Reference = unlist(out))
+})
+names(refcats) <- samples
 modres <- lapply(samples, function(p){
@@
   # Find ref cat
+  # Changed, because reference categories are now provided by researchers
   catvars <- sapply(dfmod, class) == "factor"
-  dfmod[catvars] <- lapply(dfmod[catvars], function(v){
-    tab <- table(v)
-    relevel(v, ref = names(tab)[which.max(tab)])
+  catvars <- names(catvars)[catvars]
+  refcat <- as.data.frame(refcats[[p]])
+  dfmod[catvars] <- lapply(catvars, function(c){
+    v <- dfmod[[c]]
+    relevel(v, ref = refcat$Reference[match(tolower(c), refcat$Variable)])
   })
-  # refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
-  refcat <- data.frame(Variable = names(refcats)[-1],
-                       Reference = unlist(refcats[refcats$sample == p, -1]))
-  refcat <- refcat[refcat$Variable %in% names(dfmod[catvars]), ]
-  if(nrow(refcat) > 0) names(refcat) <- c("Variable", "Reference")
   completecases <- complete.cases(dfmod)
@@
   moddat$study <- df$id_experiment[completecases]
-  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)
+  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize, iter = 10000)
   saveRDS(pma, paste0("pma_", p, ".RData"))

### 2023-02-20 codebook_dat.Rmd
add multiplier

--- 2023-01-01 codebook_dat.Rmd
@@
 ---
-title: "Codebook created on 2023-01-01 at 2023-01-01 17:14:20"
+title: "Codebook created on 2023-02-20 at 2023-02-20 10:30:46"
 output: github_document
@@
 ## Dataset description
-The data contains 20 cases and 24 variables.
+The data contains 465 cases and 21 variables.
 

### 2023-02-20 manuscript/manuscript.Rmd
add multiplier

@@
 dat <- dat[!is.na(dat$yi), ]
-
+dat$yi <- dat$yi * dat$multiplier
+dat[["multiplier"]] <- NULL
 zscores <- scale(dat[["yi"]])
@@
 #if(maxz > 3.3) stop("Potential outlier in Y-space")
-#dat <- dat[!abs(zscores) > 3.3, ]
+dat <- dat[!abs(zscores) > 3.3, ]
 saveRDS(dat, "dat.RData")

### 2023-02-20 prepare_data.R

@@ -6,7 +6,7 @@
 library(worcs)
 library(tidySEM)
 library(readxl)
-f <- "20230120 SRMA Datasheet Caspar.xlsx"
+f <- "20230207 SRMA Datasheet Caspar.xlsx"
 s <- readxl::excel_sheets(f)[-c(1:2)] # Sheet 2 now contains reference categories
 
 dat <- lapply(s, function(tst){
@@ -25,7 +25,7 @@ dat <- tidySEM:::bind_list(dat)
 
 # Rename variables
 rename_vars <- read.csv("rename_variables.csv", stringsAsFactors = FALSE)
-names(dat) <- rename_vars$new[match(names(dat), rename_vars$orig)]
+names(dat)[names(dat) %in% rename_vars$orig] <- rename_vars$new[match(names(dat)[names(dat) %in% rename_vars$orig], rename_vars$orig)]
 
 # Remove redundant moderators
 dat[c('type', 'outcome')] <- NULL

### 2023-02-21 manuscript/manuscript.Rmd
add publication bias

@@
   df <- dat[dat$Sample == p, ]
+  model_pubbias <- rma(df$yi, vi = df$vi)
+  pubbias_selmodel <- metafor::selmodel(model_pubbias, type ="stepfun", steps = c(.05))
+  png(paste0("funnel_", p, ".png"))
+  metafor::funnel(model_pubbias)
+  dev.off()
+  svg(paste0("funnel_", p, ".svg"))
+  metafor::funnel(model_pubbias)
+  dev.off()
+
   pubbias <- regtest(x = df$yi, vi = df$vi)
@@
 ggsave(paste0("threelevel_ma_forest", p, ".png"), pforest, device = "png", height = (nrow(df)+2)*.2)
-res = data.frame(Variance = c("Overall ES", "V between", "V within"),
+res = data.frame(Variance = c("Overall ES", "tau2 between", "tau2 within"),
                  rbind(c(estimate = model.full$b[1,1], ci.lb = model.full$ci.lb, ci.ub = model.full$ci.ub, model.full$pval),
@@
        res = res,
-    pubbias = pubbias)     
+    pubbias = pubbias,
+    pubbias_sel = pubbias_selmodel)     
 })
@@
 ```{r, include = FALSE}
+mlm <- readRDS("mlm.RData")
 num_effect_sizes <- table(table(dat$id_experiment))
@@
 Several studies reported multiple effect sizes (`r min(as.integer(names(num_effect_sizes))) ` - `r max(as.integer(names(num_effect_sizes)))`, with most reporting 1 effect size).
+
+## Publication bias
+
+We examined publication bias using funnel plots, Egger's test, and selection models, see Iyengar, S., & Greenhouse, J.
+B.
+(1988).
+Selection models and the file drawer problem.
+Statistical Science, 3(1), 109–117.
+⁠https://doi.org/10.1214/ss/1177013012⁠
+
+Note that these methods for detecting publication bias are only valid for random effects models;
+they thus ignore the multilevel structure of the data.
+
+We conducted likelihood ratio tests to examine whether there was evidence that publications with a p-value < .05 were more likely to be published.
+
+```{r, include=TRUE}
+out = NULL
+for (i in samples) {
+  out = c(out, knit_expand('selbias_template.Rmd'))
+}
+```
+
+`r paste(knit(text = out), collapse = '\n')`
 
@@
 ```{r, results = "asis"}
-mlm <- readRDS("mlm.RData")
 tb <- read.csv("tab_threelevel.csv", stringsAsFactors = FALSE)

### 2023-02-21 manuscript/selbias_template.Rmd
add publication bias

### Pub bias {{i}}

According to the selection model, there was `r c("no", "significant")[(mlm[["{{i}}"]][["pubbias_sel"]][["LRTp"]] < .05)+1]` evidence of publication bias, LRT(2) `r report(mlm[["{{i}}"]][["pubbias_sel"]][["LRT"]])`, p `r report(mlm[["{{i}}"]][["pubbias_sel"]][["LRTp"]])`.

Egger's test for funnel plot asymmetry showed `r c("no", "significant")[(mlm[["{{i}}"]][["pubbias"]][["pval"]] < .05)+1]` evidence of publication bias, Z `r report(mlm[["{{i}}"]][["pubbias"]][["zval"]])`, p `r report(mlm[["{{i}}"]][["pubbias"]][["pval"]])`.

```{r pubbbias{{i}}}
knitr::include_graphics("funnel_{{i}}.png")
```

### 2023-02-23 codebook_dat.Rmd
update 2023-02-23 15:57:35

--- 2023-01-01 codebook_dat.Rmd
@@
 ---
-title: "Codebook created on 2023-01-01 at 2023-01-01 17:14:20"
+title: "Codebook created on 2023-02-23 at 2023-02-23 15:00:58"
 output: github_document
@@
 ## Dataset description
-The data contains 20 cases and 24 variables.
+The data contains 465 cases and 22 variables.
 

### 2023-02-23 manuscript/manuscript.Rmd
update 2023-02-23 15:57:35

@@
 library(pema)
-run_everything = FALSE
+run_everything = TRUE
 sensitivity = FALSE
@@
 tmp <- df[order(df$vi, decreasing = TRUE), ]
+tmp$paperlabel <- paste(tmp$paper, tmp$type.of.ssri.and.dose)
 df_es <- data.frame(
-    Study = ordered(tmp$paper, levels = unique(tmp$paper)),
+    Study = ordered(tmp$paperlabel, levels = unique(tmp$paperlabel)),
     y = 1:nrow(tmp),

### 2023-02-23 prepare_data.R

@@ -6,7 +6,7 @@
 library(worcs)
 library(tidySEM)
 library(readxl)
-f <- "20230207 SRMA Datasheet Caspar.xlsx"
+f <- "20230223 SRMA Datasheet Caspar.xlsx"
 s <- readxl::excel_sheets(f)[-c(1:2)] # Sheet 2 now contains reference categories
 
 dat <- lapply(s, function(tst){

### 2023-06-10 prepare_data.R
new data file

@@ -6,7 +6,7 @@
 library(worcs)
 library(tidySEM)
 library(readxl)
-f <- "20230223 SRMA Datasheet Caspar.xlsx"
+f <- "20230608 SRMA Datasheet Caspar.xlsx"
 s <- readxl::excel_sheets(f)[-c(1:2)] # Sheet 2 now contains reference categories
 
 dat <- lapply(s, function(tst){
@@ -28,7 +28,7 @@ rename_vars <- read.csv("rename_variables.csv", stringsAsFactors = FALSE)
 names(dat)[names(dat) %in% rename_vars$orig] <- rename_vars$new[match(names(dat)[names(dat) %in% rename_vars$orig], rename_vars$orig)]
 
 # Remove redundant moderators
-dat[c('type', 'outcome')] <- NULL
+dat[c('type', 'outcome', "type of ssri and dose")] <- NULL
 
 # Recode type
 dat$nexp <- as.integer(dat$nexp)

### 2023-06-13 manuscript/manuscript.Rmd
fix HED, add dose to forest plots

@@
 tmp <- df[order(df$vi, decreasing = TRUE), ]
-tmp$paperlabel <- paste(tmp$paper, tmp$type.of.ssri.and.dose)
+tmp$paperlabel <- paste(tmp$paper, tmp$type_ssri_and_dose)
 df_es <- data.frame(

### 2023-06-13 prepare_data.R

@@ -10,7 +10,7 @@ f <- "20230608 SRMA Datasheet Caspar.xlsx"
 s <- readxl::excel_sheets(f)[-c(1:2)] # Sheet 2 now contains reference categories
 
 dat <- lapply(s, function(tst){
-  tmp <- as.data.frame(readxl::read_xlsx(path = f, sheet = tst))
+  tmp <- as.data.frame(readxl::read_xlsx(path = f, sheet = tst, na = c("", "NA")))
   names(tmp) <- tolower(names(tmp))
   tmp$test <- tst
   renam <- c("mean difference experimental group" = "mean experimental group",
@@ -28,7 +28,7 @@ rename_vars <- read.csv("rename_variables.csv", stringsAsFactors = FALSE)
 names(dat)[names(dat) %in% rename_vars$orig] <- rename_vars$new[match(names(dat)[names(dat) %in% rename_vars$orig], rename_vars$orig)]
 
 # Remove redundant moderators
-dat[c('type', 'outcome', "type of ssri and dose")] <- NULL
+dat[c('type', 'outcome')] <- NULL
 
 # Recode type
 dat$nexp <- as.integer(dat$nexp)
